---
title: "Power Analysis"
author: Jade Yonehiro & Jessica Waltmon
output: html_document
---

This script runs the power analysis for Jessica Waltmon's honors thesis project evaluating how stress mindsets related to academic stress and engagement during the COVID-19 pandemic.   

References:  
(Basic power analysis tutorial)[https://cran.r-project.org/web/packages/pwr/vignettes/pwr-vignette.html]

# Set up
```{r}
library(knitr)
library(pwr)
```

# Analysis

We will run a power analysis for a linear (regression) model or an f-test model. 

Conventional effect sizes for all tests in the pwr package:  
____________________________________________________  
Test	                    | small	| medium | large |  
____________________________________________________  
tests for proportions (p) |	0.2	  | 0.5	   | 0.8   |  
tests for means (t)       |	0.2	  | 0.5	   | 0.8   |  
chi-square tests (chisq)	| 0.1	  | 0.3	   | 0.5   |  
correlation test (r)	    | 0.1	  | 0.3	   | 0.5   |  
anova (anov)	            | 0.1	  | 0.25	 | 0.4   |  
general linear model (f2)	| 0.02	| 0.15	 | 0.35  |   
____________________________________________________  

__ pwr.fr.test __
u = numerator degrees of freedom: the number of coefficients (predictors) you'll have in your model (minus the intercept)  
v = demoninator degrees of freedom: The number we want to find out
f2 = the effect size (es) we want. Can use an es from a previous study or pick our lowest es of interest.
sig.level = what we want our alpha or "p-value' threshold to be (.05)
power = what power we want to achieve
```{r}
pwr.f2.test(u = 4,  v = ,
            f2 =  0.15,           # use a medium effect size
            sig.level = .05,      # Set our alpha or "p-value' threshold to .05
            power = .8 )          # Set power to 80%
```
